---
title: "p8105_hw1_yw4199"
author: "Yaduo Wang"
date: "2023-09-17"
output: github_document
---

#Problem 1

Load the moderndive library.

```{r, message = FALSE}
library("moderndive")
library("tidyverse")
```

Load the early_january_weather dataset.

```{r}
data("early_january_weather")
view(early_january_weather)
```

```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```

```{r}
mean(early_january_weather$temp)
```

Make a scatterplot of temp (y) vs time_hour (x); color points using the humid variable.

Export your scatterplot to your project directory using ggsave.

```{r}
ggplot(early_january_weather, mapping = aes(x = time_hour, y = temp, color = humid)) + geom_point()



```

Export your scatterplot to your project directory using ggsave.

```{r}
ggsave("p8105_hw1_yw4199_scatter_plot.pdf", height = 4, width = 6)
```

#Problem 2

Create a data frame

```{r}
normal_df = tibble(
  norm_samp = rnorm(10, mean = 1), 
  #a random sample of size 10 from a standard Normal distribution
  norm_samp_pos = norm_samp > 0,
  #a logical vector indicating whether elements of the sample are greater than 0
  vector = sample(letters, 10, replace = TRUE),
  #a character vector of length 10
  factor = as.factor(sample(1:3, 10, replace = TRUE))
  #a factor vector of length 10, with 3 different factor “levels”
)
```

Try to take the mean of each variable in your dataframe

```{r}
mean(pull(normal_df, norm_samp))
mean(pull(normal_df, norm_samp_pos))
mean(pull(normal_df, vector))
mean(pull(normal_df, factor))
```

For vector and factor variables they return NA because they are neither numeric or logical. 
For the first numeric variable, it returns 0.8553194; and for the second variable, since it is logical variable, it will treat F as 0 and T as 1 and then return the mean for all the values. 


Write a code chunk that applies the as.numeric function to the logical, character, and factor variables. 
```{r, message = FALSE}
norm_samp_pos_num = as.numeric(normal_df$norm_samp_pos) #convert logical variable to numeric
vector_num = as.numeric(normal_df$vector) #convert vector to numeric
factor_num = as.numeric(normal_df$factor) #convert factor to numeric
```

