---
title: "p8105_hw1_yw4199"
author: "Yaduo Wang"
date: "2023-09-17"
output: github_document
---

#Problem 1

```{r, message = FALSE}
library("moderndive") #Load the moderndive library.
library("tidyverse") #Load tidyverse library. 
```

```{r}
data("early_january_weather") #Load the early_january_weather dataset.
view(early_january_weather) #View the early_january_weather dataset.
```

Description of the dataset:
This dataset is a subset of the weather data frame from the 'nycflights13' package.
It contains hourly meteorological data for LGA, JFK, and EWR airports in January 2013.
The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.
The columns in this dataset include: `r names(early_january_weather)`, with the structure of `r str(early_january_weather)`. The mean temperature in this dataset is `r mean(early_january_weather$temp)`°F.

```{r}
?early_january_weather #accessing the dataset help file
nrow(early_january_weather) #number of rows 
ncol(early_january_weather) #number of columns
mean(early_january_weather$temp) #the mean temperature
```


```{r}
plot = ggplot(early_january_weather, mapping = aes(x = time_hour, y = temp, color = humid))+
      geom_point()+
      labs(x = "Time Hour",
            y = "Temperature",
            title = "Scatterplot of Temperature and Time Hour",
            subtitle = "Colored by Humidity"
            )
plot #Make a scatterplot of temp (y) vs time_hour (x); color points using the humid variable.

```

```{r}
ggsave("p8105_hw1_yw4199_scatter_plot.pdf", height = 4, width = 6)
#Export your scatterplot to your project directory using ggsave.
```

Describe patterns that are apparent in this plot:
This plot demonstrate the trend of the change of temperature with respect to time hour, and also consider the relation with humidity. From the plot, we can observe there is an overall upward trend, which indicates that as time in hours increases, the temperature increases. Around Jan 10 to Jan 15, it shows highest humidity under the temperature around 42 to 55 F. 

#Problem 2

Create a data frame

```{r}
normal_df = tibble(
  norm_samp = rnorm(10, mean = 1), 
  #a random sample of size 10 from a standard Normal distribution
  norm_samp_pos = norm_samp > 0,
  #a logical vector indicating whether elements of the sample are greater than 0
  character = sample(letters, 10, replace = TRUE),
  #a character vector of length 10
  factor = as.factor(sample(1:3, 10, replace = TRUE))
  #a factor vector of length 10, with 3 different factor “levels”
)
```

Try to take the mean of each variable in your dataframe

```{r}
mean(pull(normal_df, norm_samp)) #mean of norm_samp
mean(pull(normal_df, norm_samp_pos)) #mean of norm_samp_pos
mean(pull(normal_df, character)) #mean of character
mean(pull(normal_df, factor)) #mean of factor
```

For character and factor variables they return NA because they are neither numeric or logical. 
For the first numeric variable, it returns 0.8553194 this time; and for the second variable, since it is logical variable, it will treat F as 0 and T as 1 and then return the mean for all the values. 


Write a code chunk that applies the as.numeric function to the logical, character, and factor variables. 

```{r, echo = FALSE}
norm_samp_pos_num = as.numeric(normal_df$norm_samp_pos) #convert logical variable to numeric
character_num = as.numeric(normal_df$character) #convert character to numeric
factor_num = as.numeric(normal_df$factor) #convert factor to numeric

#generate mean for all the converted variables
mean(norm_samp_pos_num) 
mean(character_num)
mean(factor_num)
```
The norm_samp_pos_num generates 1s. This is because it treats TRUE as 1 and FALSE as 0, and then take the mean of it. This gives you the average of the trues. 
The character_num generates all NAs. 
The factor_num generates a series of numbers corresponding to the levels of their original vector, and its mean is 2.1, which is not meaningful.  

